Printing in a Periphery: a Quantitative Study of Finnish Knowledge Production, 1640-1828

### 2017-02-02 inst/examples/20170201-manuscript.Rmd
analysis fix

```{r octavo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
#>2) paper consumption in octavo format books
#>in Stockholm, Turku, Uppsala, Lund, Göteborg and Linköping

# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))

@@

p <- ggplot(df, aes(x = publication_year, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place), size = 2) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Paper consumption in selected cities") +
       guides(color = guide_legend(title = "Place", reverse = TRUE))
print(p)

# -----------------------------------------

#>graph of average title length in words in Stockholm, Turku, Uppsala,
#>Lund, Göteborg and Linköping. Both according to Kungliga, but if
#>possible Turku data from Fennica.

>>>>

### Octavo analysis

Paper consumption in octavo format books in Stockholm, Turku, Uppsala,
Lund, Göteborg and Linköping. Again Turku from Fennica, other cities
from Kungliga.

```{r octavo, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE))

@@

p <- ggplot(df, aes(x = publication_year, y = paper)) +
       geom_line(aes(color = publication_place), size = 1) +
       geom_point(aes(color = publication_place), size = 2) +
       xlab("Publication year") +
       ylab("Paper (sheets)") +
       ggtitle("Paper consumption in selected cities") +
       guides(color = guide_legend(title = "Place", reverse = TRUE))
print(p)
```

Average title length in words in Stockholm, Turku, Uppsala, Lund,
Göteborg and Linköping. According to Kungliga, except Turku from
Fennica. For octavos only,

```{r octavo2, echo=FALSE, message=FALSE, warning=FALSE, fig.width=10, fig.height=5}
# Take cities from Kungliga except Turku
cat <- "Kungliga"
df1 <- df0 %>% filter(publication_place %in% setdiff(cities, "Turku")) %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))

# Take cities from Fennica for Turku
cat <- "Fennica"
df2 <- df0 %>% filter(publication_place %in% "Turku") %>%
      	       filter(catalog == cat & gatherings == "8vo") %>%
	       group_by(publication_year, publication_place) %>%
	       summarise(n = n(), paper = sum(paper, na.rm = TRUE), mean_title_length = mean(title_length, na.rm = TRUE))
